

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'classic' 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Anuroop}{Gaddam}
\title{Cover Letter}                               % optional, remove / comment the line if not wanted
\address{3A, Norwood Place, Johnsonville, New Zealand, 6037}{New Zealand}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+64~(21)~046~8363}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{anuroop24@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{https://www.linkedin.com/in/anuroop24/}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{.}{.}
\date{\today}
\opening{Dear Panos Liatsis,}
\closing{Yours faithfully,}
\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I am an astute lecturer, researcher  and an electronics engineer with over 10 years of experience, and I am greatly interested in having a discussion with you about this job opening. Please find my CV attached for your review. After many years of active academic involvement in various topics of electronics and with an innate ability to combine innovative thinking with conceptual understanding and strategic mindset, I have decided to continue my career in teaching and leading R\&D projects, where I can mentor the next generation of industry professionals. To date, I have acted as a Research Fellow, Lecturer, Senior Tutor and Teaching Assistant roles at Victoria University, Waikato Institute of Technology and Massey University in New Zealand, where I have brought repeated success in the design, development, and management of numerous Electrical and Electronics courses, specifically focused on RF communication design, product design, multi-layer PCB design, and equipment-prototype creation in digital electronics. The number of recognition I have received to date prove my expert-level ability to plan, develop, and conduct lectures, and E-learning modules. With win-win collaboration with both academic institutions and industry, it is possible to implement R\&D initiatives that are innovative and contributing to the needs of the society.
\\Throughout these 10 years, I have proven this, with an outstanding track record of establishing and nurturing cooperation with electronics companies that entrusted my course students to drive their R\&D initiatives forward. In addition to supervising research methodology development, an organisation of actual experiments, and teamwork as such, I have excelled at compiling and delivering technical reports, papers, presentations. \\I hence invite you to review the attached CV to become familiar with my long list of skills, responsibilities, and achievements in more detail. I am currently looking for new career challenges and find that this role would suit my aspirations very well. I am in search of a dynamic environment where I may utilise my gained expertise and have a direct impact on the institution’s branding and awareness, with regards to top-level electronics courses and delivered R\&D initiatives. I would welcome the opportunity to meet with you for an in-depth discussion.\\
Thank you for your time and consideration.



\makeletterclosing

\end{document}


%% end of file `template.tex'.
